Heuristics and Really Hard Instances \\ for Subgraph Isomorphism Problems

### 2016-06-29 talk/talk.tex
Start IJCAI talk

\usepackage{tikz}
\usepackage{xcolor}
\usepackage{complexity}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{amsmath}                   % \operatorname
\usepackage{amsfonts}                  % \mathcal
\usepackage{amssymb}                   % \nexists
\usepackage{gnuplot-lua-tikz}          % graphs
\usepackage[vlined]{algorithm2e} % algorithms
\usepackage{centernot}
\usepackage{mathtools}
\usepackage{listings}

@@

\tikzset{vertex/.style={draw, circle, inner sep=0pt, minimum size=0.5cm, font=\small\bfseries}}
\tikzset{notvertex/.style={vertex, color=white, text=black}}
\tikzset{plainvertex/.style={vertex}}
\tikzset{vertexc1/.style={vertex, fill=uofgburgundy, text=white}}
\tikzset{vertexc2/.style={vertex, fill=uofgsandstone, text=white}}
\tikzset{vertexc3/.style={vertex, fill=uofgforest, text=white}}
\tikzset{vertexc4/.style={vertex, fill=uofgheather, text=white}}
\tikzset{edge/.style={color=black!50!white}}
\tikzset{bedge/.style={ultra thick}}
\tikzset{edged/.style={color=screengrey, dashed}}
\tikzset{edgel3/.style={color=uofgrose, ultra thick}}

@@

\setbeamerfont{block title}{size={}}
\setbeamerfont{title}{size=\large,series=\bfseries}
\setbeamerfont{section title}{size=\large,series=\mdseries}
\setbeamerfont{author}{size=\normalsize,series=\mdseries}
\setbeamercolor*{structure}{fg=uofguniversityblue}
\setbeamercolor*{palette primary}{use=structure,fg=black,bg=}
\setbeamercolor*{palette secondary}{use=structure,fg=white,bg=uofgcobalt}
\setbeamercolor*{palette tertiary}{use=structure,fg=white,bg=uofguniversityblue}
\setbeamercolor*{palette quaternary}{fg=white,bg=black}

@@

        \node [anchor=west, xshift=0.2cm] at (current page.west |- logo.west) {
            \begin{minipage}{0.65\paperwidth}\raggedright
                {\usebeamerfont{title}\usebeamercolor[white]{}\inserttitle}\\[0.1cm]
                {\usebeamerfont{author}\usebeamercolor[white]{}\scriptsize\insertauthor}
            \end{minipage}
        };
    \end{tikzpicture}
}

@@

\makeatletter
\setbeamertemplate{footline}
{%
    \begin{beamercolorbox}[colsep=1.5pt]{upper separation line foot}
    \end{beamercolorbox}
    \begin{beamercolorbox}[ht=2.5ex,dp=1.125ex,%
        leftskip=.3cm,rightskip=.3cm plus1fil]{author in head/foot}%
        \leavevmode{\usebeamerfont{author in head/foot}\insertshortauthor}%
        \hfill%
        {\usebeamerfont{institute in head/foot}\usebeamercolor[fg]{institute in head/foot}\insertshortinstitute}%
    \end{beamercolorbox}%
    \begin{beamercolorbox}[ht=2.5ex,dp=1.125ex,%
        leftskip=.3cm,rightskip=.3cm plus1fil]{title in head/foot}%
        {\usebeamerfont{title in head/foot}\insertshorttitle}%
        \hfill%
        {\usebeamerfont{frame number}\usebeamercolor[fg]{frame number}\insertframenumber~\frameofframes~\inserttotalframenumber}
    \end{beamercolorbox}%
    \begin{beamercolorbox}[colsep=1.5pt]{lower separation line foot}
    \end{beamercolorbox}
}
\makeatother

@@

\title[When is Finding Little Graphs Inside Big Graphs Hard?]{When is Finding Little Graphs \\ Inside Big Graphs Hard?}
\author[Ciaran McCreesh, Patrick Prosser and James Trimble]{\textbf{Ciaran McCreesh}, Patrick Prosser and James Trimble}

@@

\begin{nearlyplainframe}[t]{A Phase Transition}
    \only<1>{
        \input{gen-graph-phase-1}
    }

    \only<2>{
        \input{gen-graph-phase-2}
    }

    \only<3>{
        \input{gen-graph-phase-3}
    }

@@

\begin{frame}{2D Phase Transitions}

    \only<1>{
        \input{gen-graph-2d-1}
    }

    \only<2>{
        \input{gen-graph-2d-2}
    }

    \only<3>{
        \input{gen-graph-2d-3}
    }

@@

\begin{nearlyplainframe}[t]{3D Phase Transitions?}

    \only<1>{
        \input{gen-graph-3d-1}
    }

    \only<2>{
        \input{gen-graph-3d-2}
    }

@@

\begin{frame}{What About Induced?}

    \only<1>{
        \input{gen-graph-induced-2d-1}
    }

    \only<2>{
        \input{gen-graph-induced-2d-2}
    }

    \only<3>{
        \input{gen-graph-induced-2d-3}
    }

    \only<4>{
        \input{gen-graph-induced-2d-4}
    }

    \only<5>{
        \input{gen-graph-induced-2d-5}
    }
\end{frame}

\begin{nearlyplainframe}[t]{Induced in 3D?}

    \only<1>{
        \input{gen-graph-induced-3d-1}
    }

    \only<2>{
        \input{gen-graph-induced-3d-2}
    }

@@

\begin{frame}{Other Solvers?}

    \only<1>{
        \input{gen-graph-alt-1}
    }

    \only<2>{
        \input{gen-graph-alt-2}
    }

    \only<3>{
        \input{gen-graph-alt-3}
    }

@@

\begin{frame}{Reductions}

    \only<1>{
        \input{gen-graph-red-1}
    }

    \only<2>{
        \input{gen-graph-red-2}
    }

    \only<3>{
        \input{gen-graph-red-3}
    }

    \only<4>{
        \input{gen-graph-red-4}
    }

    \only<5>{
        \input{gen-graph-red-5}
    }

@@

\begin{frame}{Why the Weird Shape?}

    \only<1>{
        \input{gen-graph-shape-1}
    }

    \only<2>{
        \input{gen-graph-shape-2}
    }

    \only<3>{
        \input{gen-graph-shape-3}
    }

    \only<4>{
        \input{gen-graph-shape-4}
    }

    \only<5>{
        \input{gen-graph-shape-5}
    }

    \only<6>{
        \input{gen-graph-shape-6}
    }

\begin{frame}[plain,noframenumbering]
    \begin{tikzpicture}[remember picture, overlay]
        \node at (current page.north west) {
            \begin{tikzpicture}[remember picture, overlay]
                \fill [fill=uofguniversityblue, anchor=north west] (0, 0) rectangle (\paperwidth, -1.7cm);
            \end{tikzpicture}
        };

        \node (logo) [anchor=north east, shift={(-0.3cm,-0.2cm)}] at (current page.north east) {
            \includegraphics*[keepaspectratio=true,scale=0.55]{UoG_keyline.pdf}
        };
    \end{tikzpicture}
\end{frame}

>>>>

\usepackage{tikz}
\usepackage{xcolor}
\usepackage{complexity}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{amsmath}                   % \operatorname
\usepackage{amsfonts}                  % \mathcal
\usepackage{amssymb}                   % \nexists
\usepackage{gnuplot-lua-tikz}          % graphs
\usepackage[vlined]{algorithm2e} % algorithms
\usepackage{centernot}

@@

\tikzset{vertex/.style={draw, circle, inner sep=0pt, minimum size=0.5cm, font=\small\bfseries}}
\tikzset{notvertex/.style={vertex, color=white, text=black}}
\tikzset{plainvertex/.style={vertex}}
\tikzset{vertexc1/.style={vertex, fill=uofgburgundy, text=white}}
\tikzset{vertexc2/.style={vertex, fill=uofgsandstone, text=white}}
\tikzset{vertexc3/.style={vertex, fill=uofgforest, text=white}}
\tikzset{vertexc4/.style={vertex, fill=uofgheather, text=white}}
\tikzset{edge/.style={color=black!50!white}}
\tikzset{bedge/.style={ultra thick}}

@@

\setbeamerfont{block title}{size={}}
\setbeamerfont{title}{size=\large,series=\bfseries}
\setbeamerfont{section title}{size=\large,series=\mdseries}
\setbeamerfont{author}{size=\normalsize,series=\mdseries}
\setbeamercolor*{structure}{fg=uofguniversityblue}
\setbeamercolor*{palette primary}{use=structure,fg=black,bg=white}
\setbeamercolor*{palette secondary}{use=structure,fg=white,bg=uofgcobalt}
\setbeamercolor*{palette tertiary}{use=structure,fg=white,bg=uofguniversityblue}
\setbeamercolor*{palette quaternary}{fg=white,bg=black}

@@

        \node [anchor=west, xshift=0.2cm] at (current page.west |- logo.west) {
            \begin{minipage}{0.65\paperwidth}\raggedright
                {\usebeamerfont{title}\usebeamercolor[white]{}\inserttitle}\\[0.1cm]
                {\usebeamerfont{author}\usebeamercolor[white]{}\insertauthor}
            \end{minipage}
        };
    \end{tikzpicture}
}

@@

\makeatletter
\setbeamertemplate{footline}
{%
    \begin{beamercolorbox}[colsep=1.5pt]{upper separation line foot}
    \end{beamercolorbox}
    \begin{beamercolorbox}[ht=2.5ex,dp=1.125ex,%
        leftskip=.3cm,rightskip=.3cm plus1fil]{author in head/foot}%
        \leavevmode{\usebeamerfont{author in head/foot}\insertshortauthor}%
        \hfill%
        {\usebeamerfont{institute in head/foot}\usebeamercolor[fg]{institute in head/foot}\insertshortinstitute}%
    \end{beamercolorbox}%
    \begin{beamercolorbox}[ht=2.5ex,dp=1.125ex,%
        leftskip=.3cm,rightskip=.3cm plus1fil]{title in head/foot}%
        {\usebeamerfont{title in head/foot}\insertshorttitle}%
        \hfill%
        {\usebeamerfont{frame number}\usebeamercolor[fg]{frame number}\insertframenumber~\frameofframes~\inserttotalframenumber}
    \end{beamercolorbox}%
    \begin{beamercolorbox}[colsep=1.5pt]{lower separation line foot}
    \end{beamercolorbox}
}

@@

\title[Heuristics and Really Hard Instances for Subgraph Isomorphism Problems]{Heuristics and Really
Hard Instances \\ for Subgraph Isomorphism Problems}
\author[Ciaran McCreesh, Patrick Prosser and James Trimble]{\textbf{Ciaran McCreesh}, Patrick
Prosser and \\ James Trimble}

@@

\begin{nearlyplainframe}[t]{A Phase Transition}

    \input{gen-graph-phase}

@@

\begin{nearlyplainframe}[t]{In Two Dimensions?}

\begin{frame}{See The Paper For\ldots}

    \begin{itemize}
        \item Is this behaviour solver-independent?
        \item Estimating the phase transition location
        \item Using this to rediscover variable and value ordering heuristics
    \end{itemize}

@@

\begin{nearlyplainframe}[t]{What About Induced?}

@@

\begin{nearlyplainframe}[t]{What Changes Between 10 and 20?}

@@

\begin{nearlyplainframe}[t]{Is The Central Region Really Hard?}

\begin{nearlyplainframe}[t]{Constrainedness}

\begin{frame}{See The Paper For\ldots}

    \begin{itemize}
        \item Is this behaviour solver-independent?
            \begin{itemize}
                \item Also SAT, PB, MIP encodings, reduction to clique.
            \end{itemize}
        \item Estimating the phase transition location
        \item Using this to invent new variable and value ordering heuristics
            \begin{itemize}
                \item But something unexpected happens this time!
            \end{itemize}
    \end{itemize}

@@

\begin{frame}{Future Work}

    \begin{itemize}
        \item Other randomness models (bounded degree, regular, scale-free).
        \item Better estimates of the phase transition location for very sparse or very dense
            patterns.
            \begin{itemize}
                \item This needs a horrible variance calculation. Please get in touch if you like
                    doing this sort of thing.
            \end{itemize}
        \item Dynamic heuristics?
    \end{itemize}

@@

\begin{frame}[plain,noframenumbering]
    \begin{center}
        \vspace*{4em}
        \url{http://www.dcs.gla.ac.uk/~ciaran} \\
        \vspace{1em}
        \href{mailto:c.mccreesh.1@research.gla.ac.uk}{\nolinkurl{c.mccreesh.1@research.gla.ac.uk}} \\
    \end{center}

    \begin{tikzpicture}[remember picture, overlay]
        \node at (current page.north west) {
            \begin{tikzpicture}[remember picture, overlay]
                \fill [fill=uofguniversityblue, anchor=north west] (0, 0) rectangle (\paperwidth, -2.6cm);
            \end{tikzpicture}
        };

        \node (logo) [anchor=north east, shift={(-0.6cm,-0.6cm)}] at (current page.north east) {
            \includegraphics*[keepaspectratio=true,scale=0.7]{UoG_keyline.pdf}
        };
    \end{tikzpicture}
\end{frame}
